---
title: "Summary"
author: "Mateusz Kruszyna"
date: "5 lutego 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
```{r echo=FALSE}
invisible(capture.output(source('../src/main.R')))
```

<style type="text/css">

body{ /* Normal  */
      font-size: 18px;
  }
p {
  font-size: 20px;
}
ul {
  font-size: 18px;
}
td {  /* Table  */
  font-size: 18px;
}
h1.title {
  font-size: 38px;
  color: DarkRed;
}
h1 { /* Header 1 */
  font-size: 32px;
  color: DarkBlue;
}
h2 { /* Header 2 */
    font-size: 30px;
  color: DarkBlue;
}
h3 { /* Header 3 */
  font-size: 26px;
  font-family: "Times New Roman", Times, serif;
  color: DarkBlue;
}
code.r{ /* Code block */
    font-size: 18px;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 18px;
}
</style>
## Audition task 2018

This is a simple presentation of data from Pearson audition task in 2018. Below I will try to present the information contained in the data. 


## Short info about data

The dataset comes from a Pearson e-learning platform for English language learners. It’s an online workbook with automatically-graded activities that they used alongside a paper textbook. The activities are either assigned by the teacher as homework or completed voluntarily by learners as extra practice.

- **learner_id:** anonymized learner identifier
- **country:** country code of the learner
- **in_course:** “t” if the learner belongs to course taught by a teacher (as opposed
to studying alone)
- **chapter:** number or name of a chapter in the workbook
- **avg_score:** a learner’s avg. percentage score on all activities within a given unit
- **completion:** the percentage of activities completed in a given unit, out of all
activities available in that unit
- **inv_rate:** This is the extent to which a learner deviates from the suggested
order of activities by the pedagogy experts within a given unit. A value of zero
indicates no departure from the suggested order, a value of one indicates a
complete reversal of the order.

## How many empty values is in the set

```{r}
print(isNaCol)
```
The data set has empty values, which is not a good property, but unfortunately very real.
For the rest of the calculations, we will delete rows that do not have a learner ID (as incorrect data, because ID is necessary).

## Country (1)

```{r}
plot_country_10
```
In this graph, we can see that the largest group of students comes from Turkey and Poland occupies 3rd place.

## Country (2)

```{r}
print(country_last_1)
```
Only from Bangladesh, Portugal and 	Zimbabwe is one participant
